The serious gap laying on healthcare system in Thailand^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]

### 2022-04-05 outputs/paper/paper.Rmd
subtitle grammer edited

---
title: "The serious gap laying on healthcare system in Thailand^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]"
subtitle: "Why there exists gap between health system and mother's report for immunization"
author: 
  - SangWoong Lee
  - Young Suk
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "This paper has been examined possible variables that influenced children immunization report cases between healthcare system and mother's reports in Thailand. We have found that there existed significantly different rate regarding communities, region, education level and religion. This is important in a sense that it relates to lives as well as indication for why such gap exited. We will discuss its importance in details later in discussion session."
output:
  bookdown::pdf_document2:
    fig_caption: yes
toc: FALSE
bibliography: references.bib
---

>>>>

---
title: "The serious gap laying on healthcare system in Thailand^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]"
subtitle: "Why there existed gap between health system and mother's report for immunization"
author: 
  - SangWoong Lee
  - Young Suk
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "This paper has been examined possible variables that influenced children immunization report cases between healthcare system and mother's reports in Thailand. We have found that there existed significantly different rate regarding communities, region, education level and religion. This is important in a sense that it relates to lives as well as indication for why such gap exited. We will discuss its importance in details later in discussion session."
output:
  bookdown::pdf_document2:
    fig_caption: yes
toc: FALSE
bibliography: references.bib
---
